Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-11-30 Article/article.tex
Moving Article files

\section{Classification model for fuzzy rules}
For each of these attributes $x_{i}(i=1\cdots n)$ there is three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use that function to express that not all parameters are needed in a rule.
Thus we can generalise rules as follow :

@@

\section{Applying Genetic Algorithm}

@@

>>>>

\section{Fuzzy Logic}
\subsection{Classification model for fuzzy rules}
For each of these attributes $x_{i}(i=1\cdots n)$ there is three fuzzy sets that are denoted A(i,S), A(i,M), A(i,L), respectively for Small, Medium and Large.
Let's define \textbf{p} as the mapping function from $\{1\cdots s(s\leq4)\}$ to $\{1\cdots4\}$, with $\forall x\neq y, p(x)\neq p(y)$. We use that function to express that not all parameters are needed in a rule.
Thus we can generalise rules as follow :

@@

\section{Genetic Algorithm}

\subsection{Presentation}

@@

\subsection{The fitness function}

According to the law of the fittest, the best individuals have more chance breeding and transmiting their genes. But what does it mean for an individual to be fit?\\
For this work, we define the fitness function as the accuracy of prediction of an individual given a test data.

\section{Implementation}

Optimization : cache individual rule fitnesses\\
Set of rules : may be rules that are incorrect

\section{Results and Conclusion}
